Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-11-22 latex/paper.tex
将2lhex全部改为2l3;调整图像，避免label重叠;删除NEGF的部分

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-20 22:20:51
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Surface reconstruction is found to have substantial influence on the intensity and anisotropy of thermal conductivity. The relationship between the thermal conductivity  and the length of three kinds of bilayer silicene along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a). The absolute value of the thermal conductivity shows a large gap between these different surface reconstructions. The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2lhex structure are around $5W/mK$. 2l2 and 2lhex structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$. The thermal conductivity and anisotropy of multilayer silicene is shown in TABLE.\ref{tab:table1}.   The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicene. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

@@

On the other hand, the size effect of the thermal conductivity anisotropy is obvious in 2l1 but not in the others. As shown in FIG.\ref{fig:chi}, thermal conductivity in 2l1 is almost isotropic  in the case of short length (10 - 1000 $\angstrom$). When the length is above 1000  $\angstrom$), thermal conductivity become inceasingly anisotropic. This is essentially due to the difference acoustic branch along different directions whose mean free path are rather large, which is caused by phonon scattering of umklapp process. However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents. The anisotropy in 2lhex is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2lh & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

For the structures of two layers the anisotropy mainly comes from low frequency phonons while that of layer number more than fore are contributed from high frequency phonons. The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2lhex have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction. For the other structures except 3l1, the low frequency region exhibits little anisotropy while the high frequency thermal condcutivity of zigzag contribution is larger than that of armchair direction. Besides, the curves show much similarity for 4l1,5l1 and 6l1, suggesting a common mechanism of the anisotropy of them.

@@

The phonon lifetimes are the main factor of anisotropy in two layer structures while they are less essential in that of structures with more than three layers. When calutating phonon lifetimes, only three-phonon scattering process are considered,which consists of two types of scattering processes, within one of which  two phonons vanish and one phonon be created and the other type is one phonon transform to two phonons. Both of them are possible to have result phonons with q point outside Brillouin boundry, which must be fold back to Brillouin zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$). So this process is called Umpack process( U process). And of cause there exist  situation that none of the three q points outside the Brillouin boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process. If there's no U process the thermal conductivity could be as large as possible, so this process gives the dominent contribution to thermal resistance. The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014} considering only the relaxation time approxmition(RTA). We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value. The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The values are averaged for frequency bins to reduce complexity. The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2lh has reverse relation. However the anitropy of lifetime  is quite obvious in two layers structures , where lifetime of armchair direction is larger almost through all the frequency, while there's not much anisotropy in multilayer structures expcet in the 4THz-7THz range of 4l1 structure.

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/transmission}
  \caption{\label{fig:transmission} (color online)The anisotropic transmission function of the structures. The structure identifiers are labeled at top-left of each subplot. the transmission along zigzag direction is ploted as black curve while that of armchair direction is filled. The y range of each subplot is normalized to the max value within the graph.}
\end{figure}

Not only group velocity,but also phonon transmission clearly show that  localization of ballistic contribution from long wave phonons dominant the anisotropy of the structures with layers more than three.To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.The transmission function can be expressed as
\begin{equation}
  \begin{split}
    \Theta(\omega)= Tr(
    \mathbf{\widetilde{k}}_{a\alpha}
    Im(\mathbf{g}_{\alpha\alpha})
    \mathbf{\widetilde{k}}_{\alpha a}
    \mathbf{G}_{a b}^*\\
    \mathbf{\widetilde{k}}_{b\beta}
    Im(\mathbf{g}_{\beta\beta})
    \mathbf{\widetilde{k}}_{\beta b}
    \mathbf{G}_{b a}
    )
  \end{split}
\end{equation}
where $\mathbf{\widetilde{k}}_{a\alpha}$,$\mathbf{\widetilde{k}}_{\alpha a}$ represents for the interaction between left lead and center region and its transposition,  $\mathbf{\widetilde{k}}_{b\beta}$,$\mathbf{\widetilde{k}}_{\beta b}$ the interaction between center and right lead. $\mathbf{g}$ and $\mathbf{G}$ the retarded Green's function of the leads and center rigion.$Tr$ and $Im$ means trace and imaginary function. Transmission function represents for the number of channels of a given frenquency. The more chanels means larger capability of thermal transportation. The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions. The y-axis value of each panel is scaled for a more convinient comparison of transmission in the tow directions. The steps in the curves are  characterisic of perfection of the structure. Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of  2l1 is perfectly stepwise because of the perfect bonding and the absence of disorder.Transmission of both directions of 2l1 ,2l2(not show here) and 2lh are close,especially that of 2l2 are exactly the same due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure such as 3l1,4l1,5l1 and 6l1 where transmissioin is larger in zigzag direction than in armchair. This trends is quite consist with that of the thermal conducivity so transmission indeed has large effection on the difference of thermal conductivity. The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this contributes a lot to the anisotropy of the thermal transportation.

@@

By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2lh structure) and the anisotropy can be as high as 41.1\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicene 2lh has good thermoelectric properties. In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased. The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity and NEGF transmission function. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 10:59:16
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Surface reconstruction is found to have substantial influence on the intensity and anisotropy of thermal conductivity. The relationship between the thermal conductivity  and the length of three kinds of bilayer silicene along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a). The absolute value of the thermal conductivity shows a large gap between these different surface reconstructions. The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2l3 structure are around $5W/mK$. 2l2 and 2l3 structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$. The thermal conductivity and anisotropy of multilayer silicene is shown in TABLE.\ref{tab:table1}.   The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicene. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

@@

On the other hand, the size effect of the thermal conductivity anisotropy is obvious in 2l1 but not in the others. As shown in FIG.\ref{fig:chi}, thermal conductivity in 2l1 is almost isotropic  in the case of short length (10 - 1000 $\angstrom$). When the length is above 1000  $\angstrom$), thermal conductivity become inceasingly anisotropic. This is essentially due to the difference acoustic branch along different directions whose mean free path are rather large, which is caused by phonon scattering of umklapp process. However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents. The anisotropy in 2l3 is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2l3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

For the structures of two layers the anisotropy mainly comes from low frequency phonons while that of layer number more than fore are contributed from high frequency phonons. The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2l3 have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction. For the other structures except 3l1, the low frequency region exhibits little anisotropy while the high frequency thermal condcutivity of zigzag contribution is larger than that of armchair direction. Besides, the curves show much similarity for 4l1,5l1 and 6l1, suggesting a common mechanism of the anisotropy of them.

@@

The phonon lifetimes are the main factor of anisotropy in two layer structures while they are less essential in that of structures with more than three layers. When calutating phonon lifetimes, only three-phonon scattering process are considered,which consists of two types of scattering processes, within one of which  two phonons vanish and one phonon be created and the other type is one phonon transform to two phonons. Both of them are possible to have result phonons with q point outside Brillouin boundry, which must be fold back to Brillouin zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$). So this process is called Umpack process( U process). And of cause there exist  situation that none of the three q points outside the Brillouin boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process. If there's no U process the thermal conductivity could be as large as possible, so this process gives the dominent contribution to thermal resistance. The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014} considering only the relaxation time approxmition(RTA). We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value. The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The values are averaged for frequency bins to reduce complexity. The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2l3 has reverse relation. However the anitropy of lifetime  is quite obvious in two layers structures , where lifetime of armchair direction is larger almost through all the frequency, while there's not much anisotropy in multilayer structures expcet in the 4THz-7THz range of 4l1 structure.

@@

@@

By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2l3 structure) and the anisotropy can be as high as 41.1\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicene 2l3 has good thermoelectric properties. In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased. The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity and NEGF transmission function. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
